---
title: 'Case Stusy #2'
author: "Blayne Chapman"
date: "2022-09-29"
output: 
  html_document:
    keep_md: true
---

Case Study #2

Upload the tidyerse package.
```{r}
library(tidyverse)
```

Bring in our data and look at it.
```{r}
urlfile="https://github.com/WJC-Data-Science/DTS350/raw/master/coral.csv"
mydata <- read_csv(url(urlfile))

#lets see what it looks like.
head(mydata)
tail(mydata)
str(mydata)
dim(mydata)
```

Create a Graph that shows what coral bleaching has done over time. 
```{r}
ggplot(data = mydata, aes(x = Year, y = Value, fill = Event)) +
  facet_wrap(~Entity, nrow = 3, scales = "free") +
  geom_col() +
  labs(title = "Coral Bleaching Events", 
       subtitle = "The number of moderate (up to 30% of corals affected) and severe bleaching events (more than 30% corals) measured at 100 \nfixed global locations.", 
       caption = "Source: Hughes, T. P., et al. (2018). Spatial and temporal patterns of mass bleaching of corals in the Anthropocene. Science. \nOurWorldInData.org/biodiversity ? CC BY") +
  theme(legend.title = element_blank(), legend.justification = c(0, 1), 
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        plot.caption = element_text(hjust = 0, size = 8, color = 'gray40'),
        plot.title = element_text(size = 16, family = 'serif', color = "grey37", margin = margin(t = 1)),
        plot.subtitle = element_text(size = 8, color = "grey40"), 
        axis.ticks.x = element_line(color = "black"),
        axis.ticks.y = element_line(color = "white"),
        axis.text.y = element_text(color = "grey 40"),
        axis.text.x = element_text(color = "grey40"),
        panel.background = element_rect(fill = "white"),
        panel.grid.major.y = element_line(color = "gray", linetype = "dotted"))

```

In this visulaization you can see all the locations of the number of accidents per year that occurd in those locations. As we can see that in the west atlantic we see the most amount of bleaching. based on the data we see a slight increase of the bleaching as time goes on but noting that shows a trend saying it becoming "more of a problem" than it was. 
